Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-07-23 paperDraft.tex
start on assurance section

\subsubsection{Exponential Model}
In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an
exponential distribution with a failure rate parameter $\lambda_{ij}$.
Introducing notation,
\begin{align}
y_{ijk}\mid\lambda_{ij}\sim Exp(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
are the number of failures of vehicle $i$ failure mode $j$. The number of
failure modes is assumed fixed and known \textit{a priori}.

@@

\subsubsection{Weibull Model}
The exponential model is by far the most common parametric distribution used in
reliability modeling because of its desirable math mathematical properties and
simple interpretations.   Despite its common uses the assumption of a constant
failure rate over time is rarely justifiable.  It has been well documented
(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2 http://www.nap.edu/catalog/9655.html)
the issues that can arise when this assumption is violated.  We will now
consider the same hierarchical model structure while using the Weibull
distribution for each miles between failure observation.
\begin{align}
y_{ijk}\mid\lambda_{ij}\kappa_{i}\sim Weibull(\lambda_{ij}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{align}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\kappa_{j}$.  The exponential is a special
case of the Weibull, when $\kappa = 1$.
\\
It should be noted that we are currently indexing both $\rho$ and $\kappa$, only
by $j$ and not $i$, in other words we are assuming a single shape and rate
change parameter for each failure mode across vehicles.  All of these parameters
could also be indexed by $i$ and modeled hierarchical or with some combination
of both.  This is something we will omit for this paper but hope to explore in
the future.  One special case we will discuss is when a single shape parameter
can be assumed across all failure modes.  When this is justifiable it can
greatly simplify test planning calculations, as we will show in the assurance
testing section.

@@

\subsection{Assurance Test Planning}
Assurance Testing
consumer and producer risk

\subsubsection{Traditional Approach}
no producer risk

\subsubsection{Bayesian Approach}

@@

>>>>

\subsubsection{Exponential Model}
In Test Phase 1, we assume the vehicle miles at failure, $y$, follow an
exponential distribution with a failure rate parameter $\lambda_{ij}$.
Introducing notation,
\begin{equation}
f(y_{ijk}|\lambda_{ij})=\lambda_{ij} \exp(-\lambda_{ij}
y_{ijk}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{equation}
where $y_{ijk}$ are the miles between failure for vehicle $i$ failure mode $j$,
$v$ is the number of vehicles, $s$ is the number of failure modes, and $n_{ij}$
are the number of failures of vehicle $i$ failure mode $j$. The number of
failure modes is assumed fixed and known \textit{a priori}.

@@

\subsubsection{Weibull Model}
The exponential model is by far the most common parametric distribution used in
reliability modeling because of its desirable math mathematical properties and
simple interpretations.   Despite its common uses the assumption of a constant
failure rate over time is rarely justifiable.  It has been well documented
(Statistics, Testing, and Defense Acquisition: Background Papers chapter - 2
http://www.nap.edu/catalog/9655.html) the issues that can arise when this
assumption is violated.  We will now consider the same hierarchical model
structure while using the Weibull distribution.  Now we assume that the failure
times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
parameter $\lambda$ and shape parameter $\gamma$, with probability density
function
\begin{equation}
f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i} y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij}
y_{ijk}^{\gamma_{i}}), \quad i = 1,2,..,v \quad j=1,2,..,s \quad k=1,2,..,n_{ij}
\end{equation}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.
\\
It should be noted that we are currently indexing both $\rho$ and $\gamma$, only
by $j$ and not $i$, in other words we are assuming a single shape and rate
change parameter for each failure mode across vehicles.  All of these parameters
could also be indexed by $i$ and modeled hierarchical or with some combination
of both.  This is something we will omit for this paper but hope to explore in
the future.  One special case we will discuss is when a single shape parameter
can be assumed across all failure modes.  When this is justifiable it can
greatly simplify test planning calculations, as we will show in the assurance
testing section.

@@

\subsection{Assurance Test Planning}
In this section inferences learned from the first three phases of testing will
be used to develop a test plan for the next phase.  Here the objective is to
demonstrate that at a desired level of confidence, the system will meet or
exceed a specified requirement. The methods to be employed will be similar to
the assurance testing as discussed by Hamada et al. ~\cite{ref2}. Bayesian
assurance tests are used to insure that the reliability of an item meets or
exceeds a specified requirement with a desired probability. Although
practitioners often use ``assure'' and ``demonstrate'' synonymously, Meeker and
Escobar ~\cite{ME04} distinguish between reliability demonstration and
reliability assurance testing. A \emph{reliability demonstration test} is
essentially a classical hypothesis test, which uses only the data from the test
to assess whether the reliability-related quantity of interest meets or exceeds
the requirement. A \emph{reliability assurance test}, however, uses
supplementary data and information in order to testing as efficient as possible.

In both classical and Bayesian test planning scenario we are interested in
controlling error rates while minimizing the resources required for testing.  In
the DoD acquisition process the error rates will be referenced in terms of risk.
\textit{Consumer risk} which considers the event of purchasing a product that
does not meet reliability requirements.  \textit{Producer risk} which considers
the event of a product with acceptable reliability failing a given test and not
being considered for purchase.  Introducing the notation for this section, In
the JLTV case study we will be determining how many miles on test $t_0$, are
required and how many system failures to allow $c$, before the product is
considered unacceptable.  We will let $\pi$ represent  the system reliability at
a given time. It is common to base both classical and Bayesian test plans on two
specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
\leq  \pi_0$.  Although the precise definition of ARL and RRL differ between the
classical and Bayesian test criteria, we use them in an equivalent way.

\subsubsection{Reliability Demonstration Test}
Traditional methods do not use any past data for determining the testing
proceedure.  The only rely on distributional assumptions and asymptoic results.

\subsubsection{Reliability Assurance Test}

With Bayesian statistical approach we can incorperate the supplementary data
from previous testing phases with the hopes of minimizing the resorces needed
for testing.

@@

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
\bibitem{ref2} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz. Bayesian Reliability. Springer (2008).
\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology and Quantitative Management} 1, 1-25 (2004).
\bibitem{HWWGM13} M.\ S.\ Hamada, A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz. Bayesian binomial assurance tests for system reliability using component data. \textit{Journal of Quality Technology} 46, 24-32 (2014).
\bibitem{JGHR03} V.\ E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese. A hierarchical model for estimating the reliability of complex systems. In Bayesian Statistics, Vol. 7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\ Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University Press (2003).
\bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese, T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
for combining multilevel failure information in fault tree quantification and optimal follow-on resource allocation. \textit{Reliability Engineering and System Safety} 86, 397-405 (2004).
\bibitem{EH06} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability growth planning based on failure mode discovery and correction using AMSAA projection methodology. \textit{IEEE Proceedings of the Annual Reliability and Maintainability Symposium} (2006).
\end{thebibliography}
